Spike spectra for recurrences

### 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex
Rebuttal: More questions of reviewer 1 answered

The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
such time series are often spiky, which favors the proposed decomposition technique. But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions. 
The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree. 
A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).

@@

We discuss some more technical details in the following, which will also affect any application of the proposed method. 
First of all, the number of required basis functions 
$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ for an input signal of length $N$ is the crucial bottleneck of this approach, which is why it does not show good scaling behavior. The subsequent sparse 
regression, therefore, gets computationally intensive for $N>1,000$. Depending on the memory of the computer used, input signals $N>2,000$ usually do not work anymore. This means that signals 
often need to get downsampled as a preprocessing step (e.g., see Appendix \ref{sec_power_grid_appendix}). Second, the regularization parameter $\alpha$ for the regression is a crucial free parameter. 
As described in Sect.~\ref{sec_tau_rr_method}, our idea in this paper is to select the $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
given (Pearson) correlation coefficient $\rho_{\vec{s},\tilde{\vec{s}}}$ between the original signal $\vec{s}$ and itself. This ensures that $\alpha$ adjusts itself to the data as well as to the 
used regression method. We found that this increases the comparability of different spectra, especially when performing a running window approach in order to obtain an evolutionary spectrogram 
(Fig.~\ref{fig_laskar_spectra}). 
However, the two different sparse regression algorithms we encountered in this article (LASSO and STLS) yield different results for the same desired $\rho_{\vec{s},\tilde{\vec{s}}}$. 
Even if the spectra obtained in this way look qualitatively similar, they are not always quantitatively similar. The reason for this 
is that $\rho_{\vec{s},\tilde{\vec{s}}}$ is not a smooth function of $\alpha$ in case of STLS, due to the hard-thresholding involved \cite{Brunton2016}, which is shown in Fig.~\ref{fig_regularization}.
Third, when adopting our idea of applying the inter-spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters. 
This is not a drawback of the proposed method, but rather a drawback of the particular application method that we have heavily used in this article and which was the main motivation for developing 
the proposed method. As a very last remark, we draw attention to the fact that sparse regression can be transformed into sparse logistic regression when the signal we would like to transform is binary.

>>>>

The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
such time series are often spiky, which favors the proposed decomposition technique. But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions. 
The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree. The weights (also called modes) corresponding to the individual basis functions can also 
be called \textit{loadings} and must be determined. A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).

@@

We discuss some more technical details in the following, which will also affect any application of the proposed method. 
First of all, the number of required basis functions 
$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ for an input signal of length $N$ is the crucial bottleneck of this approach, which is why it does not show good scaling behavior. The subsequent sparse 
regression, therefore, gets computationally intensive for $N>1,000$. Depending on the memory of the computer used, input signals $N>2,000$ usually do not work anymore. This means that signals 
often need to get downsampled as a preprocessing step (e.g., see Appendix \ref{sec_power_grid_appendix}). Second, the regularization parameter $\alpha$ for the regression is a crucial free parameter. 
As described in Sect.~\ref{sec_tau_rr_method}, our idea in this paper is to select the $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
given (Pearson) correlation coefficient $\rho_{\vec{s},\tilde{\vec{s}}}$ between the original signal $\vec{s}$ and itself. This ensures that $\alpha$ adjusts itself to the data as well as to the 
used regression method. We found that this increases the comparability of different spectra, especially when performing a running window approach in order to obtain an evolutionary spectrogram 
(Fig.~\ref{fig_laskar_spectra}). 
However, the two different sparse regression algorithms we encountered in this article (LASSO and STLS) yield different results for the same desired $\rho_{\vec{s},\tilde{\vec{s}}}$. 
Even if the spectra obtained in this way look qualitatively similar, they are not always quantitatively similar. The reason for this 
is that $\rho_{\vec{s},\tilde{\vec{s}}}$ is not a smooth function of $\alpha$ in case of STLS, due to the hard-thresholding involved \cite{Brunton2016}, which is shown in Fig.~\ref{fig_regularization}.
Third, when adopting our idea of applying the inter-spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters.  
This is not a drawback of the proposed decomposition method, but rather a drawback of applying this technique to the $\tau$-recurrence rate of the system, which was the main motivation for 
developing the proposed method. As a very last remark, we draw attention to the fact that sparse regression can be transformed into sparse logistic regression when the signal we would like to transform is binary.
